---
title: "Apple Development Analysis"
author: "Maria Christodoulou"
date: "15/08/2019"
output: html_document
---

```{r setup, include=FALSE}

neededPackages <- c("haven","rprojroot","tidyverse","pscl","MASS","lmtest","RColorBrewer","lubridate","pollen","sandwich","colospace")
newPackages <- neededPackages[!(neededPackages %in% installed.packages()[,"Package"])]
if(length(newPackages)) install.packages(newPackages)
lapply(neededPackages, require, character.only = TRUE)
rm(neededPackages,newPackages)

find_root(rprojroot::is_rstudio_project)

```

## Data Import

Weather data downloaded from MET MIDAS at http://data.ceda.ac.uk/badc/ukmo-midas. I included soil temperature files, air temperature and rainfall (Daily measurements). The station nearest is FAVERSHAM 757 (details here: http://archive.ceda.ac.uk/cgi-bin/midas_stations/station_details.cgi.py?id=757&db=midas_stations) 

The years needed are 2013 and 2014. For temperature, columns are as follows: http://artefacts.ceda.ac.uk/badc_datadocs/ukmo-midas/TD_Table.html

Growing season from 2013/06/10 to 2013/10/07

```{r temperature}
temperature2013 <- read_delim(file.path("Data", "midas_tempdrnl_201301-201312.txt"), delim = ",", col_names =FALSE)

colnames(temperature2013)<-c("OB_END_TIME","ID_TYPE","ID","OB_HOUR_COUNT","VERSION_NUM","MET_DOMAIN_NAME","SRC_ID","REC_ST_IND","MAX_AIR_TEMP",
                             "MIN_AIR_TEMP","MIN_GRSS_TEMP","MIN_CONC_TEMP","MAX_AIR_TEMP_Q","MIN_AIR_TEMP_Q","MIN_GRSS_TEMP_Q","MIN_CONC_TEMP_Q",
                             "METO_STMP_TIME","MIDAS_STMP_ETIME","MAX_AIR_TEMP_J", "MIN_AIR_TEMP_J","MIN_GRSS_TEMP_J","MIN_CONC_TEMP_J")
head(temperature2013)

temperature2013 %>% mutate(SRC_ID=as.integer(SRC_ID)) %>% filter(SRC_ID==757) %>% 

  mutate(VERSION_NUM=as.integer(VERSION_NUM)) %>% filter(VERSION_NUM==1) %>%
  
  mutate(MAX_AIR_TEMP_Q=as.integer(MAX_AIR_TEMP_Q)) %>% filter(MAX_AIR_TEMP_Q=="1") %>%
  
  filter(OB_END_TIME>ymd(20130610)) %>%
  
  filter(OB_END_TIME<ymd(20131008)) %>%
  
  mutate(MAX_AIR_TEMP=as.double(MAX_AIR_TEMP))%>%
  
  mutate(MIN_AIR_TEMP=as.double(MIN_AIR_TEMP))->temperature2013GrowingSeason

temperature2014 <- read_delim(file.path("Data", "midas_tempdrnl_201401-201412.txt"), delim = ",", col_names =FALSE)

colnames(temperature2014)<-c("OB_END_TIME","ID_TYPE","ID","OB_HOUR_COUNT","VERSION_NUM","MET_DOMAIN_NAME","SRC_ID","REC_ST_IND","MAX_AIR_TEMP",
                             "MIN_AIR_TEMP","MIN_GRSS_TEMP","MIN_CONC_TEMP","MAX_AIR_TEMP_Q","MIN_AIR_TEMP_Q","MIN_GRSS_TEMP_Q","MIN_CONC_TEMP_Q",
                             "METO_STMP_TIME","MIDAS_STMP_ETIME","MAX_AIR_TEMP_J", "MIN_AIR_TEMP_J","MIN_GRSS_TEMP_J","MIN_CONC_TEMP_J")
head(temperature2014)

temperature2014 %>% mutate(SRC_ID=as.integer(SRC_ID)) %>% filter(SRC_ID==757) %>% 

  mutate(VERSION_NUM=as.integer(VERSION_NUM)) %>% filter(VERSION_NUM==1) %>%
  
  mutate(MAX_AIR_TEMP_Q=as.integer(MAX_AIR_TEMP_Q)) %>% filter(MAX_AIR_TEMP_Q=="1") %>%
  
  filter(OB_END_TIME>ymd(20140515)) %>%
  
  filter(OB_END_TIME<ymd(20141110)) %>%
  
  mutate(MAX_AIR_TEMP=as.double(MAX_AIR_TEMP))%>%
  
  mutate(MIN_AIR_TEMP=as.double(MIN_AIR_TEMP))->temperature2014GrowingSeason

```

# Linear data import, 2013



```{r linear 2013}

adam2013<-read_delim(file.path("Data/LM2013", "adam.txt"), delim = "\t", col_names =TRUE)

beacon2013<-read_delim(file.path("Data/LM2013", "beacon.txt"), delim = "\t", col_names =TRUE)

boiken2013<-read_delim(file.path("Data/LM2013", "boiken.txt"), delim = "\t", col_names =TRUE)

bovarde2013<-read_delim(file.path("Data/LM2013", "bovarde.txt"), delim = "\t", col_names =TRUE)

catshead2013<-read_delim(file.path("Data/LM2013", "catshead.txt"), delim = "\t", col_names =TRUE)

fuji2013<-read_delim(file.path("Data/LM2013", "fuji.txt"), delim = "\t", col_names =TRUE)

kaiser2013<-read_delim(file.path("Data/LM2013", "kaiser.txt"), delim = "\t", col_names =TRUE)

limoncella2013<-read_delim(file.path("Data/LM2013", "limoncella.txt"), delim = "\t", col_names =TRUE)

present2013<-read_delim(file.path("Data/LM2013", "present.txt"), delim = "\t", col_names =TRUE)

red2013<-read_delim(file.path("Data/LM2013", "red.txt"), delim = "\t", col_names =TRUE)

rheinischer2013<-read_delim(file.path("Data/LM2013", "rheinischer.txt"), delim = "\t", col_names =TRUE)

wheeler2013<-read_delim(file.path("Data/LM2013", "wheeler.txt"), delim = "\t", col_names =TRUE)

adam2013 %>% count(Week)

linear2013<-bind_rows(adam2013,beacon2013,boiken2013,bovarde2013,catshead2013,fuji2013,kaiser2013,
          limoncella2013,present2013,red2013,rheinischer2013,wheeler2013)

rm(adam2013,beacon2013,boiken2013,bovarde2013,catshead2013,fuji2013,kaiser2013,
          limoncella2013,present2013,red2013,rheinischer2013,wheeler2013)

```

# Linear 2014

```{r linear 2014}
boiken2014<-read_delim(file.path("Data/LM2014", "Boiken2014.txt"), delim = "\t", col_names =TRUE)

bovarde2014<-read_delim(file.path("Data/LM2014", "Bovarde2014.txt"), delim = "\t", col_names =TRUE)

fuji2014<-read_delim(file.path("Data/LM2014", "Fuji2014.txt"), delim = "\t", col_names =TRUE)

kaiser2014<-read_delim(file.path("Data/LM2014", "Kaiser2014.txt"), delim = "\t", col_names =TRUE)

present2014<-read_delim(file.path("Data/LM2014", "Present2014.txt"), delim = "\t", col_names =TRUE)

wheeler2014<-read_delim(file.path("Data/LM2014", "Wheeler2014.txt"), delim = "\t", col_names =TRUE)

linear2014<-bind_rows(boiken2014,bovarde2014,fuji2014,kaiser2014,present2014,wheeler2014)

rm(boiken2014,bovarde2014,fuji2014,kaiser2014,present2014,wheeler2014)
```

## Growing degree days calculations

```{r gdds}
GDD2013base5<-gdd(tmax = temperature2013GrowingSeason$MAX_AIR_TEMP, tmin = temperature2013GrowingSeason$MIN_AIR_TEMP, tbase = 5, tbase_max = 30)

GDD2014base5<-gdd(tmax = temperature2014GrowingSeason$MAX_AIR_TEMP, tmin = temperature2014GrowingSeason$MIN_AIR_TEMP, tbase = 5, tbase_max = 30)

GDD2013base10<-gdd(tmax = temperature2013GrowingSeason$MAX_AIR_TEMP, tmin = temperature2013GrowingSeason$MIN_AIR_TEMP, tbase = 10, tbase_max = 30)

GDD2014base10<-gdd(tmax = temperature2014GrowingSeason$MAX_AIR_TEMP, tmin = temperature2014GrowingSeason$MIN_AIR_TEMP, tbase = 10, tbase_max = 30)

View(temperature2013GrowingSeason %>% dplyr::select(OB_END_TIME, MIN_AIR_TEMP, MAX_AIR_TEMP) %>%
       mutate(Diff=MAX_AIR_TEMP-MIN_AIR_TEMP))


```

#Homogenising two years

```{r merging years}

linear2013 %>% mutate(Day=Week*7) %>% 
  dplyr::select("Culivar", "Day", "Replicate","Diameter","Length","Weight") %>%
  rename("Cultivar"="Culivar") %>%
  mutate(Date=ymd(20130610)+Day) %>%
  dplyr::select(-"Day") %>%
  dplyr::select("Cultivar","Date", everything())->linear2013

linear2014 %>% dplyr::select("Cultivar", "Day", "Replicate","Diameter","Length","Weight") %>%
  mutate(Date=ymd(20140515)+Day) %>%
  dplyr::select(-"Day") %>%
  dplyr::select("Cultivar","Date", everything())->linear2014

as.Date(temperature2013GrowingSeason$OB_END_TIME)

GDD2013<-bind_cols(Date=as.Date(temperature2013GrowingSeason$OB_END_TIME),GDDbase5=GDD2013base5,GDDbase10=GDD2013base10)

GDD2014<-bind_cols(Date=as.Date(temperature2014GrowingSeason$OB_END_TIME),GDDbase5=GDD2014base5,GDDbase10=GDD2014base10)

left_join(linear2013,GDD2013)
left_join(linear2014,GDD2014)

full_join(left_join(linear2013,GDD2013),left_join(linear2014,GDD2014))->linearMorphometricsGDD


```

model
```{r Adams}
cor((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$Weight, (linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5)

full_model<- lm(Weight ~ GDDbase5, data =  (linearMorphometricsGDD%>%filter(Cultivar=="Adam")))
summary(full_model)
quadratic_model <- lm(Weight ~ GDDbase5 + I(GDDbase5^2), data =  (linearMorphometricsGDD%>%filter(Cultivar=="Adam")))
summary(quadratic_model)

order_id <- order((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5)
plot((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5,((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$Weight))

lines(x = (linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5[order_id], 
      y = fitted(quadratic_model)[order_id],
      col = "red", 
      lwd = 2)


quadratic_model2 <- lm(log(Weight) ~ GDDbase5 + I(GDDbase5^2), data =  (linearMorphometricsGDD%>%filter(Cultivar=="Adam")))
summary(quadratic_model2)
BIC(quadratic_model)
BIC(quadratic_model2)


order_id <- order((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5)
plot((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5,log(((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$Weight)))

lines(x = (linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5[order_id], 
      y = fitted(quadratic_model2)[order_id],
      col = "red", 
      lwd = 2)


single_log_model <- lm(log(Weight) ~ GDDbase5, data =  (linearMorphometricsGDD%>%filter(Cultivar=="Adam")))
summary(single_log_model)
plot((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5,log(((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$Weight)))

lines(x = (linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5[order_id], 
      y = fitted(single_log_model)[order_id],
      col = "red", 
      lwd = 2)

double_log_model <- lm(log(Weight) ~ log(GDDbase5), data =  (linearMorphometricsGDD%>%filter(Cultivar=="Adam")))
summary(double_log_model)
plot(log((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5),log(((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$Weight)))

lines(x = log((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5[order_id]), 
      y = fitted(double_log_model)[order_id],
      col = "red", 
      lwd = 2)


BIC(quadratic_model)
BIC(quadratic_model2)
BIC(single_log_model)
BIC(double_log_model)
plot(quadratic_model)
plot(double_log_model)

library(MASS)

log_sqrt_model <- lm(log(Weight) ~ sqrt(GDDbase5), data =  (linearMorphometricsGDD%>%filter(Cultivar=="Adam")))
summary(log_sqrt_model)
plot(log_sqrt_model)

BIC(log_sqrt_model)
sqrt_sqrt_model <- lm(sqrt(Weight) ~ sqrt(GDDbase5), data =  (linearMorphometricsGDD%>%filter(Cultivar=="Adam")))
summary(sqrt_sqrt_model)
BIC(sqrt_sqrt_model)
    
log_1oversqrt_model <- lm(log(Weight) ~ 1/sqrt(GDDbase5), data =  (linearMorphometricsGDD%>%filter(Cultivar=="Adam")))
summary(log_1oversqrt_model)

BIC(quadratic_model)
BIC(quadratic_model2)
BIC(single_log_model)
BIC(double_log_model)
BIC(log_sqrt_model)
BIC(sqrt_sqrt_model)
BIC(log_1oversqrt_model)


plot(log((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5),log(((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$Weight)))

lines(x = log((linearMorphometricsGDD%>%filter(Cultivar=="Adam"))$GDDbase5[order_id]), 
      y = fitted(double_log_model)[order_id],
      col = "red", 
      lwd = 2)
plot(double_log_model)




```
```{r}
double_log_model_all <- lm(log(Weight) ~ log(GDDbase5), data =linearMorphometricsGDD)
summary(double_log_model_all)
plot(log(linearMorphometricsGDD$GDDbase5),log(linearMorphometricsGDD$Weight))

order_id_all <- order(linearMorphometricsGDD$GDDbase5)

lines(x = log(linearMorphometricsGDD$GDDbase5[order_id_all]), 
      y = fitted(double_log_model_all)[order_id_all],
      col = "red", 
      lwd = 2)
BIC(double_log_model_all)
plot(double_log_model_all)

asymptotic_weight<-nls(log(Weight)~SSasymp(GDDbase5, a, b, c),data = linearMorphometricsGDD)

summary(asymptotic_weight)
BIC(double_log_model_all)
BIC(asymptotic_weight) # Worse than double log

coeftest(double_log_model_all,vcov=vcovHC, type = "HC1")

```

```{r length}


linearMorphometricsGDD %<>% mutate(Length=ifelse(year(Date)==2013,Length*10,Length)) %>%
  mutate(Diameter=ifelse(year(Date)==2013,Diameter*10,Diameter))
plot(log(linearMorphometricsGDD$GDDbase5),log(linearMorphometricsGDD$Length))

double_log_model_length<-lm(log(Length)~log(GDDbase5), data=linearMorphometricsGDD)

plot(double_log_model_length) 

summary(double_log_model_length)

asymptotic_length<-nls(log(Length)~SSasymp(GDDbase5, a, b, c),data = linearMorphometricsGDD)

summary(asymptotic_length)
BIC(double_log_model_length)
BIC(asymptotic_length) # Worse than double log




```

```{r diameter}

plot(log(linearMorphometricsGDD$GDDbase5),log(linearMorphometricsGDD$Diameter))

double_log_model_diameter<-lm(log(Diameter)~log(GDDbase5), data=linearMorphometricsGDD)

plot(double_log_model_diameter) 

summary(double_log_model_diameter)

plot(log(linearMorphometricsGDD$GDDbase5),log(linearMorphometricsGDD$Diameter))

lines(x = log(linearMorphometricsGDD$GDDbase5[order_id_all]), 
      y = fitted(double_log_model_diameter)[order_id_all],
      col = "red", 
      lwd = 2)

asymptotic_diameter<-nls(log(Diameter)~SSasymp(GDDbase5, a, b, c),data = linearMorphometricsGDD)

summary(asymptotic_diameter)
BIC(double_log_model_diameter)
BIC(asymptotic_diameter) # Worse than double log

ggplot(linearMorphometricsGDD,aes(x=log(GDDbase5),y=log(Diameter)))+
  theme_bw()+
  geom_point(shape=20)+
  geom_line(col="grey45",aes(x=log(linearMorphometricsGDD$GDDbase5[order_id_all]), y=fitted(double_log_model_diameter)[order_id_all]))+
  xlab("Logarithm of Growing Degree Days (base 5)")+
  ylab("Logarithm of Diameter (in mm)")+
  ggtitle("Log-log linear regression for Diameter")

ggplot(linearMorphometricsGDD,aes(x=log(GDDbase5),y=log(Length)))+
  theme_bw()+
  geom_point(shape=20)+
  geom_line(col="grey45",aes(x=log(linearMorphometricsGDD$GDDbase5[order_id_all]), y=fitted(double_log_model_length)[order_id_all]))+
  xlab("Logarithm of Growing Degree Days (base 5)")+
  ylab("Logarithm of Length (in mm)")+
  ggtitle("Log-log linear regression for Length")

ggplot(linearMorphometricsGDD,aes(x=log(GDDbase5),y=log(Weight)))+
  theme_bw()+
  geom_point(shape=20)+
  geom_line(col="grey45",aes(x=log(linearMorphometricsGDD$GDDbase5[order_id_all]), y=fitted(double_log_model_all)[order_id_all]))+
  xlab("Logarithm of Growing Degree Days (base 5)")+
  ylab("Logarithm of Weight (in g)")+
  ggtitle("Log-log linear regression for Weight")


```

# Geometric Size:

```{r GM data import}
adamGM2013<-read_delim(file.path("Data/GM2013", "adam.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Adam")

beaconGM2013<-read_delim(file.path("Data/GM2013", "beacon.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Beacon")

boikenGM2013<-read_delim(file.path("Data/GM2013", "boiken.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Boiken")

bovardeGM2013<-read_delim(file.path("Data/GM2013", "bovarde.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Bovarde")

catsheadGM2013<-read_delim(file.path("Data/GM2013", "catshead.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Catshead")

fujiGM2013<-read_delim(file.path("Data/GM2013", "fuji.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Fuji")

kaiserGM2013<-read_delim(file.path("Data/GM2013", "kaiser.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Kaiser")

limoncellaGM2013<-read_delim(file.path("Data/GM2013", "limoncella.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Limoncella")

presentGM2013<-read_delim(file.path("Data/GM2013", "present.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Present")

redGM2013<-read_delim(file.path("Data/GM2013", "red.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Red")

rheinischerGM2013<-read_delim(file.path("Data/GM2013", "rheinischer.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Rheinischer")

wheelerGM2013<-read_delim(file.path("Data/GM2013", "wheeler.txt"), delim = "\t", col_names =TRUE) %>% mutate(Cultivar="Wheeler")

geometric2013<-bind_rows(adamGM2013,beaconGM2013,boikenGM2013,bovardeGM2013,catsheadGM2013,fujiGM2013,kaiserGM2013,
          limoncellaGM2013,presentGM2013,redGM2013,rheinischerGM2013,wheelerGM2013)

rm(adamGM2013,beaconGM2013,boikenGM2013,bovardeGM2013,catsheadGM2013,fujiGM2013,kaiserGM2013,
          limoncellaGM2013,presentGM2013,redGM2013,rheinischerGM2013,wheelerGM2013)

geometric2013 %>% filter(Week>1) %>% mutate(Day=Week*7) %>% 
  dplyr::select("Cultivar", "Day", "Individual","CentroidSize") %>%
  mutate(Date=ymd(20130610)+Day) %>%
  dplyr::select(-"Day") %>%
  dplyr::select("Cultivar","Date", everything())->geometric2013

left_join(geometric2013,GDD2013)->geometricMorphometricsGDD


```

Centroid size

```{r}

order_id_all_geom <- order(geometricMorphometricsGDD$GDDbase5)
plot(geometricMorphometricsGDD$GDDbase5,geometricMorphometricsGDD$CentroidSize)
double_log_model_centroid<-lm(log(CentroidSize)~log(GDDbase5), data=geometricMorphometricsGDD)
plot(double_log_model_centroid)
centroidLog_log_model_centroid<-lm(log(CentroidSize)~(GDDbase5), data=geometricMorphometricsGDD)

plot(centroidLog_log_model_centroid) 

model_centroid<-lm(CentroidSize~GDDbase5, data=geometricMorphometricsGDD)
summary(model_centroid)

boxcox(model_centroid, lambda = seq(0,1, 0.001))
plot(model_centroid) 
plot(double_log_model_centroid)
plot(centroidLog_log_model_centroid) 

bptest(double_log_model_centroid)
plot(log(geometricMorphometricsGDD$GDDbase5),log(geometricMorphometricsGDD$CentroidSize))
lines(lines(x = log(geometricMorphometricsGDD$GDDbase5[order_id_all_geom]), 
      y = fitted(double_log_model_centroid)[order_id_all_geom],
      col = "red", 
      lwd = 2))
summary(double_log_model_centroid)



quadratic_model_centroid <- lm(CentroidSize ~ GDDbase5 + I(GDDbase5^2), data = geometricMorphometricsGDD)
summary(quadratic_model_centroid)
asymptotic_centroid<-nls(log(CentroidSize)~SSasymp(GDDbase5, a, b, c),data = geometricMorphometricsGDD)

summary(asymptotic_centroid)
plot(asymptotic_centroid)
BIC(asymptotic_centroid)
BIC(double_log_model_centroid)


ggplot(geometricMorphometricsGDD,aes(x=log(GDDbase5),y=log(CentroidSize)))+
  theme_bw()+
  geom_point(shape=20)+
  geom_line(col="grey45",aes(x=log(geometricMorphometricsGDD$GDDbase5[order_id_all_geom]), y=fitted(double_log_model_centroid)[order_id_all_geom]))+
  geom_line(col="blueviolet", aes(x = log(geometricMorphometricsGDD$GDDbase5[order_id_all_geom]), 
      y = fitted(asymptotic_centroid)[order_id_all_geom]), linetype=8)+
  xlab("Logarithm of Growing Degree Days (base 5)")+
  ylab("Logarithm of Centroid size")+
  ggtitle("Centroid Size")


geometricMorphometricsGDD

```

# graphics

```{r}

library(colorspace)

q12 <- sequential_hcl(12, palette = "Viridis")

linearMorphometricsGDD

ggplot(linearMorphometricsGDD,aes(x=log(GDDbase5),y=log(Diameter),col=Cultivar))+
  theme_bw()+
  geom_point(shape=20)+
  geom_line(col="grey45",aes(x=log(linearMorphometricsGDD$GDDbase5[order_id_all]), y=fitted(double_log_model_diameter)[order_id_all]))+
  geom_line(col="blueviolet", aes(x = log(linearMorphometricsGDD$GDDbase5[order_id_all]),
      y = fitted(asymptotic_diameter)[order_id_all]), linetype=8)+
  xlab("Logarithm of Growing Degree Days (base 5)")+
  xlab("Logarithm of Growing Degree Days (base 5)")+
  ylab("Logarithm of Diameter (in mm)")+
  scale_color_manual(values=q12)

ggsave("DiameterColours.svg",  width = 7.29, height = 9)

ggplot(linearMorphometricsGDD,aes(x=log(GDDbase5),y=log(Length),col=Cultivar))+
  theme_bw()+
  geom_point(shape=20)+
  geom_line(col="grey45",aes(x=log(linearMorphometricsGDD$GDDbase5[order_id_all]), y=fitted(double_log_model_length)[order_id_all]))+
  geom_line(col="blueviolet", aes(x = log(linearMorphometricsGDD$GDDbase5[order_id_all]),
      y = fitted(asymptotic_length)[order_id_all]), linetype=8)+
  xlab("Logarithm of Growing Degree Days (base 5)")+
  ylab("Logarithm of Length (in mm)")+
  scale_color_manual(values=q12)

ggsave("LengthColours.svg",  width = 7.29, height = 9)

ggplot(linearMorphometricsGDD,aes(x=log(GDDbase5),y=log(Weight),col=Cultivar))+
  theme_bw()+
  geom_point(shape=20)+
  geom_line(col="grey45",aes(x=log(linearMorphometricsGDD$GDDbase5[order_id_all]), y=fitted(double_log_model_all)[order_id_all]))+
  geom_line(col="blueviolet", aes(x = log(linearMorphometricsGDD$GDDbase5[order_id_all]),
      y = fitted(asymptotic_weight)[order_id_all]), linetype=8)+
  xlab("Logarithm of Growing Degree Days (base 5)")+
  ylab("Logarithm of Weight (in g)")+
  scale_color_manual(values=q12)

ggsave("WeightColour.svg",  width = 7.29, height = 9)

ggplot(geometricMorphometricsGDD,aes(x=log(GDDbase5),y=log(CentroidSize),col=Cultivar))+
  theme_bw()+
  geom_point(shape=20)+
  geom_line(col="grey45",aes(x=log(geometricMorphometricsGDD$GDDbase5[order_id_all_geom]), y=fitted(double_log_model_centroid)[order_id_all_geom]))+
  geom_line(col="blueviolet", aes(x = log(geometricMorphometricsGDD$GDDbase5[order_id_all_geom]),
      y = fitted(asymptotic_centroid)[order_id_all_geom]), linetype=8)+
  xlab("Logarithm of Growing Degree Days (base 5)")+
  ylab("Logarithm of Centroid size")+
  scale_color_manual(values=q12)

ggsave("CentroidSizeColour.svg",  width = 7.29, height = 9)

linearMorphometricsGDD %>% filter(Date=="2013-09-23")
bind_cols(temperature2013GrowingSeason,GDD5=GDD2013base5) %>% dplyr::select(OB_END_TIME,GDD5)
bind_cols(temperature2014GrowingSeason,GDD5=GDD2014base5) %>% dplyr::select(OB_END_TIME,GDD5)
gdds<-c(1098.55,1217.35,1353.75,1362.85,1516.65)

as_tibble(gdds) %>% mutate(logs=log(gdds))
c(gdds[1],log(gdds[-5]))
log(gdds)-c(gdds[1],log(gdds[-5]))

((gdds[2]*100)/gdds[1])-100 #difference between 09/09/2013 and 23/09/2013
(log(gdds[3])*100)/log(gdds[2])-100 #difference between 23/09/2013 and 07/10/2013
(log(gdds[5])*100)/log(gdds[4])-100 #difference between 08/09/2014 and 22/09/2014


geometricMorphometricsGDD

```

```{r}
linearMorphometricsGDD %>% group_by(Date,Cultivar) %>% count() %>% arrange(Cultivar)
```
#Interpretation

```{r}
a=log((100 + 1.5)/100)
exp(a*0.437) #Length 0.437: 10% increase in GDD to 1.04% increase in Length
exp(a*0.511) #Diameter 0.511 : 10% increase in GDD to 1.05% increase in Diameter
exp(a*1.389) #Weight 1.389 : 10% increase in GDD to 1.14% increase in Weight
exp(a*0.488) #Centroid Size 0.488 10% increase in GDD to 1.05% increase in Weight



```


